Reliable feature point matching

### 2013-08-06 text/thesis.tex
Added introduction to applications

@@

The results of the comparison can be seen in Table~\ref{table:nnd} where
\emph{MMC} improves performance by 8.05\% over the original framework 
using \emph{Ratio} to match images.

% About near duplicates mention how we can't use ransac to find inliers 
% since we can't necessarily construct a homography between two images

There are two important steps to image stitching which i- Describe in 
general why better matching improves the results and speed on a broad 
range of different computer vision problems
 - Elaborate on why the two examples where chosen (are there any 
 particular reasons?)
 - Near duplicate detection
 - Panorama application

>>>>

In many areas of computer vision matching local feature points is a key 
component, and matching algorithms have applications in problems such as
scene matching, object recognition, near duplicate detection and 
panorama recognition. To show the practical applications of the proposed 
matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
improve existing methods in near duplicate detection and panorama 
recognition. These two problems were chosen because they both involve 
matching images that might or might not overlap. These cases requires 
matching algorithms that limit false positives since e.g. returning the 
top $n$ matches for any given image pair would make it hard to 
distinguish adjacent or duplicate images from non-adjacent or dissimilar
image pairs. Near duplicate detection also constraints normal matching 
algorithms from relying on geometric assumptions, since we have very few
guarantees between two potential near duplicates that they should be 
matched using any particular geometric heuristic. In this section, we 
will first see \emph{MMC} applied to panorama recognition and alignment,
and next \emph{MMC} and \emph{MM} applied to near duplicate detection.

@@

The results of the comparison can be seen in Table~\ref{table:nnd} where
\emph{MMC} improves performance by 8.05\% over the original framework 
using \emph{Ratio} to match images. For comparison, the performance 
improvement of \emph{PhotoCluster} compared to XMatch 
\cite{zhao2009scale}, the second best performing algorithm on the 
California-nd dataset according to \cite{vas2013cluster} is 2.52\%.
